descriptive anaysis

### 2020-06-12 src/bbData2020.Rmd
Revert "Revert "fix Rmd conflicts, fix paths to data temp outputs, knit html, remove .gitignore from temp data folder.""
This reverts commit ceca99313e95ed5b36d6eef6837fbcc9debc08f2.

Plot2019 + geom_line()
Plot2020 <- ggplot(Wks2020, aes(dateOnly, tests20))
Plot2020 + geom_line()
HrDateCount19 <- count(Wks2019, dateOnly, hour)
HrDateCount20 <- count(Wks2020, dateOnly, hour)
names(HrDateCount19)[3] <- "testFreq19"
names(HrDateCount20)[3] <- "testFreq20"
Wks2019 <- left_join(Wks2019, HrDateCount19)
Wks2020 <- left_join(Wks2020, HrDateCount20)
TimeVar2019n <- timeVariation(Wks2019, pollutant = "testFreq19", 
                    statistic = "mean")
TimeVar2020n <- timeVariation(Wks2020, pollutant = "testFreq20", 
                              statistic = "mean")
#save files
write.csv(Wks2019, "Wks2019.csv")
write.csv(Wks2020, "Wks2020.csv")

>>>>

Plot2019 + geom_line()
Plot2020 <- ggplot(Wks2020, aes(dateOnly, tests20))
Plot2020 + geom_line()
HrDateCount19 <- count(Wks2019, dateOnly, hour)
HrDateCount20 <- count(Wks2020, dateOnly, hour)
names(HrDateCount19)[3] <- "testFreq19"
names(HrDateCount20)[3] <- "testFreq20"
Wks2019 <- left_join(Wks2019, HrDateCount19)
Wks2020 <- left_join(Wks2020, HrDateCount20)
TimeVar2019n <- timeVariation(Wks2019, pollutant = "testFreq19", 
                    statistic = "mean")
TimeVar2020n <- timeVariation(Wks2020, pollutant = "testFreq20", 
                              statistic = "mean")
#save files
out.Wks2019 <- paste(path, "./data/temp/Wks2019.csv", sep = "")
out.Wks2020 <- paste(path, "./data/temp/Wks2020.csv", sep = "")
write.csv(Wks2019, out.Wks2019)
write.csv(Wks2020, out.Wks2020)
```
